\subsection*{Grants}
\begin{itemize}[itemsep=1pt, parsep=0pt,leftmargin=*]
\item[] \textbf{PI}. Co-design of gas turbine and carbon capture for affordable low carbon power. MIT Energy Initiative. Total \$150,000. 2026-2027.
\item[] \textbf{PI}. Towards End-to-End Process Intelligence: GPU-Accelerated Parameter Optimization. MIT Initiative for New Manufacturing. Total \$50,000. 2026.
\item[] \textbf{Co-PI}. Optimal Design of Carbon Capture Units under Uncertainties in Feed Compositions and Operational Conditions. Department of Energy and Shell. \$175,000 allocation. 
\item[] \textbf{Co-PI}. Digital Twins for Sustainable Low-Cost EV Batteries: Real-Time Monitoring and Charging Optimization. Tata-MIT Alliance. 
\item[] \textbf{Co-PI}. Watts v/s Bytes: Energy Storage Impact Analysis on Flexible Computing Loads. MIT Energy Initiative. 2025-2026.
\item[] \textbf{PI}. Data-Driven Modeling of the Dynamics of Battery Degradation Process for Degradation-Aware Decision-Making in Grid-Scale Storage Systems.  Research Support Committee. Total \$90,000. 2025-2026.
\item[] \textbf{PI}. Characterizing the Trade-Off between CO2 Capture Rate and Energy Efficiency in Amine-Based Carbon Capture under Variable Feed Conditions. MIT Energy Initiative. Total \$250,000. 2025-2027.
\item[] \textbf{PI}. Optimal Utilization Strategies of Utility-Scale Battery Storage: Slowing Down Degradation in the Face of Complex Physics and Uncertainties. MIT Energy Initiative. Total \$150,000. 2024-2026.
\item[] \textbf{PI}. Multi-Scale Production Cost Modeling for Optimal Storage Investment. MIT Energy Initiative. Total \$100,000. 2024-2025.
\item[] \textbf{PI}. Analyzing the Ripple Effect of Consumer Flexibility on Utility Scale Energy System Investments. EQUINOR. Total \$304,524. 2024-2025.
\end{itemize}

%%% Local Variables:
%%% mode: LaTeX
%%% TeX-master: "shin.tex"
%%% End:
